---
title: "Ask and prepare"
output: html_notebook
---
```{r}
library(tidyverse)
library(dplyr)
```
#Ask 

The questions I have to answer are: 

I have to analyze smart device usage data in order to gain insight into how consumers use non-Bellabeat smart
devices. I then have to select one Bellabeat product to apply these insights to. 

The follwing questoins should guide my analysis: 

1. What are some trends in smart device usage?
2. How could these trends apply to Bellabeat customers?
3. How could these trends help influence Bellabeat marketing strategy?

Products to chose from:

1. Bellabeat app: The Bellabeat app provides users with health data related to their activity, sleep, stress,
menstrual cycle, and mindfulness habits. This data can help users better understand their current habits and
make healthy decisions. The Bellabeat app connects to their line of smart wellness products.

2. Leaf: Bellabeat’s classic wellness tracker can be worn as a bracelet, necklace, or clip. The Leaf tracker connects
to the Bellabeat app to track activity, sleep, and stress.

3.  Time: This wellness watch combines the timeless look of a classic timepiece with smart technology to track user
activity, sleep, and stress. The Time watch connects to the Bellabeat app to provide you with insights into your
daily wellness.

4. Spring: This is a water bottle that tracks daily water intake using smart technology to ensure that you are
appropriately hydrated throughout the day. The Spring bottle connects to the Bellabeat app to track your
hydration levels.

5. Bellabeat membership: Bellabeat also offers a subscription-based membership program for users.
Membership gives users 24/7 access to fully personalized guidance on nutrition, activity, sleep, health and
beauty, and mindfulness based on their lifestyle and goals.

The stakeholders are: 

1. Urška Sršen: Bellabeat’s cofounder and Chief Creative Officer

2. Sando Mur: Mathematician and Bellabeat’s cofounder; key member of the Bellabeat executive team

3. Bellabeat marketing analytics team: A team of data analysts responsible for collecting, analyzing, and reporting
data that helps guide Bellabeat’s marketing strategy.

#Prepare 
The dataset is on the following link: https://www.kaggle.com/datasets/arashnic/fitbit

```{r}

file_list_m3_to_m4 <- list.files(path = "./data/Fitabase Data 3.12.16-4.11.16", pattern = "*.csv", full.names = TRUE)
file_list_m4_to_m5 <- list.files(path = "./data/Fitabase Data 4.12.16-5.12.16", pattern = "*.csv", full.names = TRUE)

```

```{r}

print(file_list_m3_to_m4)

```

```{r}

file_list_m3_to_m4 %>% 
  map(~ read_csv(.x) %>% glimpse())

```



```{r}

# Check column names for each dataframe
lapply(df_list_m3_to_m4, colnames)

```

```{r}



```

